Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/Virgo Network

### 2013-06-20 doc/paper.tex
Added half of Vivien's comments (still want to add a couple of the suggestions) and added Tyson's paragraps

Of course one must distinguish between the detection of 
such events, and the precision measurement of the relevant physical parameters.
The detection of BNS systems will be performed with a matched filtering approach.  
By comparing the data stream with a bank of theoretical templates, the 
 time-series data can be searched for candidate signals at a sufficiently
  rapid rate to analyze months of data.  When the overlap between one of the template waveforms and the 
detector output is sufficiently large (97\%), a detection candidate is found.  However,
the parameter space of these signals can be highly degenerate, with several 
locations in parameter space corresponding to nearly identical waveforms.  In 
order to fully realize the science potential of these instruments, we must 
perform a full exploration of the parameter space for each detection.  By 
analyzing the parameter space of each candidate with a Bayesian inference technique, 
 we will be able to make precise, scientifically meaningful
statements about the physics of these systems.  To 
that end, we employ a Markov-Chain Monte Carlo sampling algorithm, 
\texttt{lalinference\_mcmc}, included in the LIGO Application Library parameter
estimation code, \texttt{LALInference}, to analyze the parameter space of BNS systems.

@@

We begin by introducing a Bayesian formalism for parameter estimation. 
%Before offering a brief derivation of the FIM, a few preliminary
%techniques must be introduced.  First,
We assume that the time-domain signal in a gravitational-wave
network can be written as a combination of a gravitational
waveform $h_0$ and the noise of the detector $n$.  We further assume
that this noise is stationary and Gaussian with zero mean.  Therefore,
the detector output is simply
\begin{equation}
s = n + h_0 .
\label{SignalAddition}
\end{equation}
Since the noise model is Gaussian, we can write the
probability of a specific signal realization $s$ as proportional to the probability
that the residual is Gaussian distributed once the waveform has been subtracted
\begin{align}
  p(s | \thpara) &\propto \exp\left[-\frac{1}{2}\left<n|n
    \right>\right] \nonumber \\ &= \exp\left[-\frac{1}{2}\left < s -
    h(\thpara) | s-h(\thpara)\right >\right] ,
  \label{likelihood}
\end{align}
where $\thpara$ is the set of parameters for the template
waveforms, and $p(s | \thpara)$ is the likelihood of the signal $s$ given the parameters $\thpara$.
  The inner product, $\left< ~|~ \right> $, is defined using the noise
spectrum of the detectors as
\begin{equation}
  \left<a|b\right> \equiv 4 \Re \int \frac{\tilde{a}(f)\tilde{b}^*(f)}{S_n(f)} df ,
  \label{innerProduct}
\end{equation}
where $S_n(f)$ is the one-sided power spectral density (PSD) as a function
of frequency, and $\tilde{a}(f)$ and $\tilde{b}(f)$ are the Fourier
transforms of the time-domain data $a(t)$ and $b(t)$.  If we pick a set of parameters $\thpara$ such that
$h(\thpara) = h_0$, then the posterior \eqref{posterior}
will be near a global maximum; however, the presence of noise will in
general deflect the maximum of our posterior away from the value at
$\thpara_0$. That is, in the presence of noise, there is
no guarantee that the maximum-likelihood of our signal corresponds to
the true parameters of the system.

@@

\begin{itemize}
\item uniform in component masses from $0.8M_{\odot} \leq M_{1,2} \leq 30M_{\odot}$, with a minimum chirp mass  \eqref{eqRatioCM} of 0.6 $M_{\odot}$,
\item uniform in volume, which implies a luminosity distance prior of $p(D) = D^2 dD$, and
\item uniform in all other parameters.
\end{itemize}

@@

Finally, note that the power-spectral density that defines the inner product \eqref{innerProduct} is simply 
the time-averaged sensitivity of a given detector to a specific frequency.  Ignoring non-Gaussian glitches,
 any stretch of data should contain a specific noise realization drawn from a Gaussian colored by the PSD.
   However, what we are interested in is not the parameter estimation that can occur in a specific draw
    from this probability of noises, but the uncertainties averaged over all possible noise
     realizations.\footnote{Similarly to how the Fisher matrix formalism can provide the Cramer-Rao bound averaged over
     all noise realizations} Since our noise model is assumed to be Gaussian, it is unnecessary to recover the
      parameters from a large sample of identical waveforms in different noise; we can simply assume the 
      noise \emph{is} the mean defined by the power-spectral density.  This ``zero-noise'' parameter estimation
       provides a statistical statement on the measurable uncertainties, and is what is reported here.  In Section
        \ref{noiseSection} we provide an example of parameter estimation in several non-zero noise realizations
compared to the zero-noise equivalent \carl{[TYSON WILL WRITE]}.

@@

\begin{figure*}[t!]
\centering
\includegraphics[trim=7cm 0cm 0cm 0cm, clip=true,scale=0.55]{9dpdf.pdf}
%\begin{array}{ccc} 
%\includegraphics[width=2.2in]{1dpdfs/mc.pdf} &\includegraphics[width=2.2in]{1dpdfs/eta.pdf}  & \includegraphics[width=2.2in]{1dpdfs/m1.pdf}\\
%\includegraphics[width=2.2in]{1dpdfs/time.pdf} &\includegraphics[width=2.2in]{1dpdfs/dist.pdf}  &\includegraphics[width=2.2in]{1dpdfs/iota.pdf}\\
%\includegraphics[width=2.2in]{1dpdfs/ra.pdf} & \includegraphics[width=2.2in]{1dpdfs/dec.pdf} & \includegraphics[width=2.2in]{1dpdfs/m2.pdf}
%\end{array}$
\caption{Marginalized 1D posterior probability density functions taken from a typical 
$1.4M_{\odot}/1.4M_{\odot}$ BNS system.  We have plotted each of the 9 parameters for 
our non-spinning BNS problem as stated in section \ref{waveformSection}.  Note how, 
even for parameters with excellent recovery, the peak of the 1D Gaussian is displaced from 
the injected value (in dashed red).  This is not due to a systematic bias, but is caused by the 
marginalization of a single dimension from the full 9D posterior space.  To better see this effect, 
compare the 1D PDF for $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in Figure~\label{9dPDF}}
\end{figure*}

Of the nine parameters in the domain of the waveform, only six are particularly physically
interesting: the masses of the two binaries, $M_1$ and $M_2$, the orbital inclination,
$\iota$, the angular position on the sky, $\alpha$ and $\delta$, and the luminosity 
distance of the source, $D$.  While the coalescence phase $\phi_c$, the coalescence time
$t_c$, and the wave polarization $\psi$ must be included in any parameter estimation of the 
waveform, they do not encode any information of particular astrophysical interest.
\footnote{For systems whose components are non-spinning.  The presence of intrinsic angular 
momentum will, in general, couple to the coalescence phase and wave polarization.}

In Figure~\ref{9dPDF}, we provide an example of the nine, 1-dimensional marginalized posterior 
probability density functions recovered from a single $1.4M_{\odot}/1.4M_{\odot}$ BNS system. 
 These PDFs are the typical of the type of results that will be produced by parameter estimation
  studies in the advanced  detector era.  Notice that the peak of several parameters, including the 
  chirp mass, $\chmass$,  appears to be displaced from the true values in red.  This effect is due to 
  the reduction of the  9-dimensional PDF to a series of marginalized 1-dimensional PDFs. 
   For instance, the 1-dimensional PDF for chirp mass is marginalized via

@@

Given this degeneracy, it should come as no surprise that the 2D marginalized posteriors of distance
 and inclination are the broadest of the six physically interesting parameters.  Four typical 2D PDFs are
  presented in Figure~\ref{distIotaPDF}.  Notice the bimodal uncertainty 
present in the top 2D PDF along the $\iota$ axis, due to the similarity between the evaluated
 likelihoods at $\iota$ and $\iota + \pi/2$.  As the majority of the information extracted via parameter 
 estimation is from the phase of the signal, the recovery of a posterior in $D$-$\iota$ space will be 
 limited, even during the Advanced LIGO/Virgo era; however, there if a gravitational-wave signal is 
 matched to a detected SGRB counterpart (which may occur at the rate of $\sim 3 yr^{-1}$ in Advanced LIGO/Virgo, 
 according to \cite{Metzger2013}), the optical information about the orbital inclination
 will provide an additional constraint on the D-$\iota$ space, vastly improving the luminosity distance recovery
 quoted here.

@@

  In practice, however, additional information from the wave polarization and the relative difference
  in SNR between individual detectors can break this plane-reflected degeneracy,
   leading to a bi-modal distribution with significantly more support in one mode of the PDF.
     By fitting for the sky location and the polarization simultaneously, the MCMC can often identify
   the correct mode on the sky.  For the four-detector configuration, this concern is irrelevant: even with time-of-arrival
   data alone, the HLVI network can constrain any source to a single mode on the sky.  Even then, there are still locations 
   on the sky in which two or more detectors are not sensitive to the gravitational-wave signal, distorted, non-Gaussian PDFs.

The sky location uncertainties for HLV and HLVI are shown in Figures \ref{2525SkyLocHLV}
 and \ref{2525SkyLocHLVI} respectively.  We show all four mass bins together, since in practice
  the mass of the signals has no effect on the recovery of the sky location.  Only the location on 
  the sky, the network configuration, and the other extrinsic parameters were found to be relevant.  
  In particular, notice the increase in efficiency between the HLV configuration and the HLVI 
  configuration.  In the HLV configuration, there exist points on the sky in which the signal was injected
  near the plane of the detector network.  This causes the elongated, ``banana-shaped'' PDFs seen in
  Figure \ref{2525SkyLocHLV}.  In the HLVI configuration, the plane is no longer relevant, and there are substantially
  less regions in which only two detectors see a sufficiently strong signal.  
  See \cite{Veitch2012} for a more detailed comparison of the sky-localization benefits of the HLVI 
  configuration verses the three-detector network.  As previously, the quantitative results for the two network configurations
  are reported in Table \ref{ciTableExtrinsic}.

@@

\begin{figure}[ht!]
  \centering
 \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.52]{noisePDF.pdf}
 \caption{The effects of a non-zero noise realization on the recovered PDF for five different Gaussian realizations of the Advanced LIGO noise curve.  Each PDF represents the recovery of the same $1M_{\odot}/2.5M_{\odot}$ signal in a different noise curve, picked at random from the Gaussian colored noise defined by the Advanced LIGO power spectral density.  Notice how the curve is relatively unchanged, but usually assumes a Gaussian PDF displaced from the true value.  This only holds true for glitch-free data, which is an unrealistic idealization when compared to real data.}
 \label{noisePDFs}
\end{figure}

We have performed the current analysis on zero-noise injections for two reason.  First, the results of a zero-noise 
analysis are identical to those that would be achieved by averaging the results of multiple identical injections 
in different Gaussian noise realizations, as was argued in Section \ref{waveformSection}.  The second reason is simply
that no good model exists for the true (decidedly non-Gaussian) noise that will arrive with a single detection candidate,
Each detection will occur in noisy data, with a specific realization of the PSD provided and with 
possible instrumentation and environmental glitches.  In the case of a unique Gaussian realization
of the Advanced-LIGO noise curve, each realization causes the maximum likelihood of the posterior probability 
distribution to be translated away from the true value; however, these displacements are drawn
according to the zero-noise distribution \citep{Inadequacies}.  Once averaged, the mean
uncertainties should be equal to the uncertainty drawn from the zero-noise runs.

@@

Of course, the largest concern for gravitational-wave parameter estimation will not be the specific
realization of Gaussian noise, but the effects of glitches in the data.  These time-series 
glitches have a variety of well-known and not-so-well-known physical causes in the instrument,
and can cause substantially greater errors in parameter recovery than any specific noise realizations.  This has already been addressed for the case of space-based gravitational-wave
detectors (LISA), and is currently being implemented in \texttt{lalinference\_mcmc} 
\carl{[TYSON WILL WRITE]}.

@@

\begin{table*}[t!]
\centering
\caption{Mean 65\% confidence intervals for intrinsic parameters for each of the four systems considered.  We report the confidence intervals of quantities measured, as well as the component masses and total mass.  Although the results for the 
HLV and HLVI configurations are quantitatively identical, we report them separately for consistancy.}
\begin{tabular}{lcccccccccc}

@@

Secondly, as stated above, the noise realization that we have employed here is an substantial idealization.  In practice the noise levels of Advanced LIGO and Advanced Virgo will be highly variable over time, and will \emph{not} be stationary or Gaussian, as is commonly assumed.  Unfortunately, there is no reliable or simple way to simulate the sort of non-Gaussian detector glitches and instrumentation effects that will arise in any advanced gravitational-wave detector.  Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here \carl{[TYSON WILL WRITE]}

>>>>

Of course one must distinguish between the detection of 
such events, and the precision measurement of the relevant physical parameters.
The detection of BNS systems will be performed with a matched filtering approach.  
By comparing the data stream with a bank of theoretical templates, the 
 time-series data can be searched for candidate signals at a sufficiently
  rapid rate to analyze months of data.  When the overlap between one of the template waveforms and the 
detector output is sufficiently large (97\%), a detection candidate is found.  However,
the parameter space of these signals can be highly degenerate, with several 
locations in parameter space corresponding to nearly identical waveforms.  In 
order to fully realize the science potential of these instruments, we must 
perform a full exploration of the parameter space for each detection.  By 
analyzing the parameter space of each candidate with a Bayesian inference technique, 
 we will be able to make precise, scientifically meaningful
statements about the physics of these systems.  To 
that end, we employ a Markov-Chain Monte Carlo sampling algorithm, 
\texttt{lalinference\_mcmc}, included in the LIGO Algorithm Library parameter
estimation code, \texttt{LALInference}, to analyze the parameter space of BNS systems.

@@

We begin by introducing a Bayesian formalism for parameter estimation. 
%Before offering a brief derivation of the FIM, a few preliminary
%techniques must be introduced.  First,
We assume that the time-domain signal in a gravitational-wave
network can be written as a combination of a gravitational
waveform $h_0$ and the noise of the detector $n$.  We further assume
that this noise is stationary and Gaussian with zero mean.  Therefore,
the detector output is simply
\begin{equation}
s = n + h_0 .
\label{SignalAddition}
\end{equation}
Since the noise model is Gaussian, we can write the
probability of a specific signal realization $s$ as proportional to the probability
that the residual is Gaussian distributed once the waveform has been subtracted
\begin{align}
  p(s | \thpara) &\propto \exp\left[-\frac{1}{2}\left<n|n
    \right>\right] \nonumber \\ &= \exp\left[-\frac{1}{2}\left < s -
    h(\thpara) | s-h(\thpara)\right >\right] ,
  \label{likelihood}
\end{align}
where $\thpara$ is the set of parameters for the template
waveforms, and $p(s | \thpara)$ is the likelihood of the signal $s$ given the parameters $\thpara$.
  The inner product, $\left< ~|~ \right> $, is defined using the noise
spectrum of the detectors as
\begin{equation}
  \left<a|b\right> \equiv 4 \Re \int \frac{\tilde{a}(f)\tilde{b}^*(f)}{S_n(f)} df ,
  \label{innerProduct}
\end{equation}
where $S_n(f)$ is the one-sided power spectral density (PSD) as a function
of frequency, and $\tilde{a}(f)$ and $\tilde{b}(f)$ are the Fourier
transforms of the time-domain data $a(t)$ and $b(t)$.  If we pick a set of parameters $\thpara$ such that
$h(\thpara) = h_0$, then the posterior \eqref{posterior}
will be near a global maximum; however, our choice of prior the presence of noise will in
general deflect the maximum of our posterior away from the value at
$\thpara_0$.  Therefore, the maximum posterior parameters do not necessarily 
correspond to the true parameters of the source, so when interpreting parameter
 estimation results we must consider the full posterior distribution function.

@@

\begin{itemize}
\item uniform in component masses from $0.8M_{\odot} \leq M_{1,2} \leq 30M_{\odot}$, with a minimum chirp mass  \eqref{eqRatioCM} of 0.6 $M_{\odot}$,
\item uniform in volume, which implies a luminosity distance prior of $p(D) = D^2 dD$,
\item uniform in coalescence time over the segment of data being analyzed, and
\item uniform in all other parameters, with angular parameters being flat over their corresponding domains.
\end{itemize}

@@

Finally, note that the power-spectral density that defines the inner product \eqref{innerProduct} is simply 
the time-averaged sensitivity of a given detector to a specific frequency.  Ignoring non-Gaussian glitches,
 any stretch of data should contain a specific noise realization drawn from a Gaussian colored by the PSD.
%   However, what we are interested in is not the parameter estimation that can occur in a specific draw
  %  from this probability of noises, but the uncertainties averaged over all possible noise
     realizations. Without a realistic model including the actual instrument sensitivity,
      non stationary noise, and uncertainty in the PSD we cannot 
     accurately simulate GW data to the point of making precise predictions about parameter 
     estimation capabilities.  Furthermore, the posterior distribution from a future 
     detection will be influenced by 
     the realization of the noise at the time of the detection.  Because of this, we 
     elect to focus only on the statistical 
     errors due to the flexibility of the waveforms and the expected sensitivity of 
     the advanced era detectors and suppress 
     any effects of detector noise by not including a noise realization in our simulated data.
       Consequently, what we recover with the MCMC  
     could be interpreted as the posterior distribution function for each source averaged over all
      possible (Gaussian) noise realizations 
     assuming we have the correct PSD.    \footnote{Similarly to how the Fisher matrix formalism can
      provide the Cramer-Rao bound averaged over
     all noise realizations.  Unlike a Fisher matrix study, we make no assumptions about the 
     shape of the posterior distribution function, nor the location of the peak, while still requiring a
      feasible number of MCMC runs 
     to sufficiently cover parameter space, which would not be the case had we needed to 
     average several noise-dependent results.} To check that our reported statistical errors
     are not in gross disagreement with those obtained in the presence of noise,  we selected a 
       particular simulated signal to perform parameter estimation in several noise realizations.  
       The comparison of the noise-dependent and noise-free results
       can be found in \ref{noiseSection}.

@@

\begin{figure*}[t!]
\centering
\includegraphics[trim=7cm 0cm 0cm 0cm, clip=true,scale=0.55]{9dpdf.pdf}
%\begin{array}{ccc} 
%\includegraphics[width=2.2in]{1dpdfs/mc.pdf} &\includegraphics[width=2.2in]{1dpdfs/eta.pdf}  & \includegraphics[width=2.2in]{1dpdfs/m1.pdf}\\
%\includegraphics[width=2.2in]{1dpdfs/time.pdf} &\includegraphics[width=2.2in]{1dpdfs/dist.pdf}  &\includegraphics[width=2.2in]{1dpdfs/iota.pdf}\\
%\includegraphics[width=2.2in]{1dpdfs/ra.pdf} & \includegraphics[width=2.2in]{1dpdfs/dec.pdf} & \includegraphics[width=2.2in]{1dpdfs/m2.pdf}
%\end{array}$
\caption{Marginalized 1D posterior probability density functions taken from a typical 
$1.4M_{\odot}/1.4M_{\odot}$ BNS system.  We have plotted each of the 9 parameters for 
our non-spinning BNS problem as stated in section \ref{waveformSection}.  Note how, 
even for parameters with excellent recovery, the peak of the 1D Gaussian is displaced from 
the injected value (in dashed red).  This is not due to a systematic bias, but is caused by the 
marginalization of a single dimension from the full 9D posterior space.  To better see this effect, 
compare the 1D PDF for $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in Figure~\ref{1414masses}}
\end{figure*}

Of the nine parameters in the domain of the waveform, only six are particularly physically
interesting: the masses of the two binaries, $M_1$ and $M_2$, the orbital inclination,
$\iota$, the angular position on the sky, $\alpha$ and $\delta$, and the luminosity 
distance of the source, $D$.  While the coalescence phase $\phi_c$, the coalescence time
$t_c$, and the wave polarization $\psi$ must be included in any parameter estimation of the 
waveform, they do not encode any information of particular astrophysical interest.\footnote{For systems
 whose components are non-spinning.  The presence of intrinsic angular 
momentum will, in general, couple to the coalescence phase and wave polarization.}

In Figure~\ref{9dPDF}, we provide an example of the nine, 1-dimensional marginalized posterior 
probability density functions recovered from a single $1.4M_{\odot}/1.4M_{\odot}$ BNS system. 
 These PDFs are typical of the type of results that will be produced by parameter estimation
  studies in the advanced  detector era.  Notice that the peak of several parameters, including the 
  chirp mass, $\chmass$,  appears to be displaced from the true values in red.  This effect is due to 
  the reduction of the  9-dimensional PDF to a series of marginalized 1-dimensional PDFs. 
   For instance, the 1-dimensional PDF for chirp mass is marginalized via

@@

Given this degeneracy, it should come as no surprise that the 2D marginalized posteriors of distance
 and inclination are the broadest of the six physically interesting parameters.  Four typical 2D PDFs are
  presented in Figure~\ref{distIotaPDF}.  Notice the bimodal uncertainty 
present in the top 2D PDF along the $\iota$ axis, due to the similarity between the evaluated
 likelihoods at $\iota$ and $\iota + \pi/2$.  As the majority of the information extracted via parameter 
 estimation is from the phase of the signal, the recovery of a posterior in $D$-$\iota$ space will be 
 limited, even during the Advanced LIGO/Virgo era; however, if a gravitational-wave signal is 
 matched to a detected SGRB counterpart (which may occur at the rate of $\sim 3 yr^{-1}$ in Advanced LIGO/Virgo, 
 according to \cite{Metzger2013}), the optical information about the orbital inclination
 will provide an additional constraint on the D-$\iota$ space, vastly improving the luminosity distance recovery
 quoted here.

@@

  In practice, however, additional information from the wave polarization and the relative difference
  in SNR between individual detectors can break this plane-reflected degeneracy,
   leading to a bi-modal distribution with significantly more support in one mode of the PDF.
     By fitting for the sky location and the polarization simultaneously, the MCMC can often identify
   the correct mode on the sky.  For the four-detector configuration, this concern is irrelevant: even with time-of-arrival
   data alone, the HLVI network can constrain any source to a single mode on the sky.  Even then, there are still locations 
   on the sky in which two or more detectors are not sensitive to the gravitational-wave signal, yielding
    distorted, non-Gaussian PDFs.

The sky location uncertainties for HLV and HLVI are shown in Figures \ref{2525SkyLocHLV}
 and \ref{2525SkyLocHLVI} respectively.  We show all four mass bins together, since in practice
  the mass of the signals has no effect on the recovery of the sky location for the considered BNS systems.
    Only the location on 
  the sky, the network configuration, and the other extrinsic parameters were found to be relevant.  
  In particular, notice the increase in efficiency between the HLV configuration and the HLVI 
  configuration.  In the HLV configuration, there exist points on the sky in which the signal was injected
  near the plane of the detector network.  This causes the elongated, ``banana-shaped'' PDFs seen in
  Figure \ref{2525SkyLocHLV}.  In the HLVI configuration, the plane is no longer relevant, and there are substantially
  less regions in which only two detectors see a sufficiently strong signal.  
  See \cite{Veitch2012} for a more detailed comparison of the sky-localization benefits of the HLVI 
  configuration verses the three-detector network.  As previously, the quantitative results for the two network configurations
  are reported in Table \ref{ciTableExtrinsic}.

@@

\begin{figure}[ht!]
  \centering
 \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.52]{noisePDF.pdf}
 \caption{The effects of a non-zero noise realization on the recovered PDF for five different Gaussian realizations of the 
 Advanced LIGO noise curve.  Each PDF represents the recovery of the same $1M_{\odot}/2.5M_{\odot}$ signal in a
  different noise curve, picked at random from the Gaussian colored noise defined by the Advanced LIGO power
   spectral density, while the gray-shaded curve is the zero-noise PDF.  Notice how the curve is relatively unchanged,
    but usually assumes a Gaussian PDF displaced from the true value.  This only holds true for glitch-free data, which
     is an unrealistic idealization when compared to real data.}
 \label{noisePDFs}
\end{figure}

We have performed the current analysis on zero-noise injections for two reason.  First, the results of a zero-noise 
analysis are identical to those that would be achieved by averaging the results of multiple identical injections 
in different Gaussian noise realizations, as was argued in Section \ref{waveformSection}.  The second reason is 
we are not able to predict the characteristics of realistic (often non-Gaussian) advanced detector noise.  
Attempting to do so would have little chance of being accurate while requiring a huge computational 
burden to combine the results of many MCMC runs in different noise realizations.

 In the case of a unique Gaussian realization
of the Advanced-LIGO noise curve, each realization causes the maximum likelihood of the posterior probability 
distribution to be translated away from the true value; however, these displacements are drawn
according to the zero-noise distribution \citep{Inadequacies}.  Once averaged, the mean
uncertainties should be equal to the uncertainty drawn from the zero-noise runs.

@@

Of course, the largest concern for gravitational-wave parameter estimation will not be the specific
realization of Gaussian noise, but the effects of non-Gaussianities in the data.  Techniques which build
 off of the theoretical progress made in~\cite{Allen:2002jw,Rover:2011qd,Littenberg:2010gf} for including
  glitches in our model for the data, and therefore relaxing the assumptions about stationary and Gaussian
   noise, are currently under investigation.

@@

\begin{table*}[t!]
\centering
\caption{Mean 65\% confidence intervals for intrinsic parameters for each of the four systems considered.  We report the confidence intervals of quantities measured, as well as the component masses and total mass.  Although the results for the 
HLV and HLVI configurations are quantitatively identical, we report them separately for consistency.}
\begin{tabular}{lcccccccccc}

@@

Secondly, as stated above, we have performed our study under idealized detector-noise conditions.  In practice the noise levels of Advanced LIGO and Advanced Virgo can vary with time and contain occasional excursions which are highly non-Gaussian.  Unfortunately, there is no reliable way to predict the sort of non-Gaussian detector glitches and instrumentation effects that will arise in any advanced gravitational-wave detector.  Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here.
